Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-20 aistats.tex
Add section on optimal n0

\subsection{Complementary Plots}

\rlp{Show that the optimal mu0 is larger than mu* for small n0.}

>>>>

\subsection{Optimal $\mu_0$ is larger than $\mu^*$ for small $n_0$ and small $n$}

The upper bound~\eqref{eq:MAP_rate} has a bias term that is $0$ when $\frac{mu_0}{\mu^*} = 1 + \inv{n_0}$, e.g. for large values of $n_0$, it is $\mu_0=\mu^*$ is the best prior, but for small $n_0$, one better sets larger values for $\mu_0$. In Figure~\ref{fig:optimal_n0}, we observe this behavior numerically.

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{figs/optimal_n0.pdf}
	\caption{Contours of $\expect{\KL(\nat^*, \hat \nat_n)}$  for the Gaussian variance with $n\in\{1,5,10\}$, $\mu^*=1$ and $\mu_0, n_0$ spanning $[10^{-2}, 10^2]$. We observe that the line $\frac{\mu_0}{\mu^*} = 1 + \inv{n_0}$ coincides with the bottom valley of this landscape.
	}
	\label{fig:optimal_n0}
\end{figure}
